Meta-analysis fear learning

### 2022-02-21 manuscript/manuscript.Rmd
DUmmy coding

As the models contained only categorical variables but no meaningful reference category,
we estimated a model _without_ an intercept,
and instead included an equal number of dummies to the number of unique categories (ANOVA specification instead of regression specification).
This way, the effect of each dummy reflects the mean value for that category.
To further aid interpretability, the dependent variable (effect size) was centered around the random-effects meta-analysis estimated overall effect.
This changes the interpretation of the effect of each dummy, such that it reflects the deviation of that category from the overall effect size as estimated in the random-effects meta-analysis.
If a dummy variable has a significant effect, that means that that group's mean differs significantly from the overall mean.

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  modmat <- model.matrix(~.-1, df[mods])
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_centered <- df$yi - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_centered,
             vi = df$vi,
             mods = modmat, intercept = F)
  vifs <- vif(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

  moddat <- data.frame(yi = yi_centered, vi = df$vi, modmat)
  moddat$study <- 1
  standardize <- list(center = rep(0, (ncol(moddat)-3)),
                      scale = rep(1, (ncol(moddat)-3)))

  pma <- brma(yi ~-1+., study = "study", data = moddat, standardize = standardize)

  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
  moddatvi <- moddat$vi
  moddat <- moddat[, -which(colnames(moddat) == "vi")]
  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
  list(rma = tabres,
       brma = sumpma,
       mc = resmc)
})
names(modres) <- processes
saveRDS(modres, "modres.RData")
```

>>>>

To examine the effect of a categorical variable,
a reference category must be chosen.
Dummy variables encode the difference between each remaining category and this reference category.
When examining the results,
the intercept represents the expected effect size for a study that falls within the reference category for all categorical variables.
The effect of dummy variables represents the difference of that category with the reference category.
If a dummy variable has a significant effect, that means that that group's mean differs significantly from the reference category's mean (i.e., from the intercept).

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  catvars <- sapply(df, class) == "factor" & names(df) %in% mods
  df[catvars] <- lapply(df[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  names(refcat) <- c("Variable", "Reference")
  modmat <- model.matrix(~., df[mods])
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

  moddat <- data.frame(yi = yi_notcentered, vi = df$vi, modmat)
  moddat$study <- 1
  standardize <- list(center = rep(0, (ncol(moddat)-3)),
                      scale = rep(1, (ncol(moddat)-3)))

  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)

  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
  moddatvi <- moddat$vi
  moddat <- moddat[, -which(colnames(moddat) == "vi")]
  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
  list(rma = tabres,
       brma = sumpma,
       mc = resmc,
       refcat = refcat)
})
names(modres) <- processes
saveRDS(modres, "modres.RData")
```
